A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-02-15 paper/paper.tex
dropouts plot
see XXX in eda.r for mismatch of hgc

@@

\caption{Males dropouts' work experience in the original and refreshed data. Each point represents the work experience of individuals (identified by the ID) in the corresponding survey period. We can see that the correlation is reasonably high between them even though the exactly same figure could not be obtained.}\label{fig:compare-xp-sw}
\end{figure}

>>>>

\begin{verbatim}
#> # A tibble: 2 x 3
#>   hgc   hgc12     n
#>   <chr> <chr> <int>
#> 1 12TH  8TH       1
#> 2 8TH   12TH    243
\end{verbatim}

@@

\caption{Males dropouts' work experience in the original and refreshed data. Each point represents the work experience of individuals (identified by the ID) in the corresponding survey period. We can see that the correlation is reasonably high between them even there are different values for many individuals.}\label{fig:compare-xp-sw}
\end{figure}
